Country-Level Impact of Education on Entrepreneurship

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

Drawing from Inglehart research ????????? MAIN BIB 2000 ????????, we understand the period between 0 and 20 years of age to be a defining time in terms of personal values and personality construction, thus compulsory education, generally between 6 and 16 years of age, can prove of key importance in the building up of one's self-confidence. We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions. This assumption draws from Boyd and Vozikis's ??????? MAIN BIB ???????? stating how entrepreneurial intentions are at least partially the result of thought processes, which "underlie the creation of formal business plans, opportunity analysis, and goal-directed behaviour". Boyd and Vosikis also assert that individual self-efficacy "influences the development of both entrepreneurial intentions and actions or behaviours". To assert this, they rely on Fishbein and Ajzen 1975 ?????? MAIN BIB ???????? who illustrate the relation between beliefs and behaviour as follows:

>>>>

Our focus on the education systems stems partly from experience and from Inglehart research ????????? MAIN BIB 2000 ???????? . Indeed, we understand the period between 0 and 20 years of age to be a defining time in terms of personal values and personality construction, thus compulsory education, generally between 6 and 16 years of age, can prove of key importance in the building up of one's self-confidence. We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions. This assumption draws from Boyd and Vozikis's ??????? MAIN BIB ???????? stating how entrepreneurial intentions are at least partially the result of thought processes, which "underlie the creation of formal business plans, opportunity analysis, and goal-directed behaviour". Boyd and Vosikis also assert that individual self-efficacy "influences the development of both entrepreneurial intentions and actions or behaviours". To assert this, they rely on Fishbein and Ajzen 1975 ?????? MAIN BIB ???????? who illustrate the relation between beliefs and behaviour as follows:
